\plaintitle

### 2017-01-10 drafts/labor/abstract.tex
chinmay's suggestions integrated

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
  \externaldocument{complexity}
  \externaldocument{relationships}
  \externaldocument{decomposition}
}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\onlyinsubfile{\plaintitle}
\begin{abstract}
The internet is empowering the rise of
crowd work,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has attempted to predict
the socio--technical outcomes of this shift, especially addressing three questions:
\begin{inlinelist}
\item \nameref{sec:complexity}?,
\item \nameref{sec:decomposition}?, and
\item \nameref{sec:relationships}?
\end{inlinelist}
In this paper, we look to the historical scholarship on piecework
--- a similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern on--demand work.
We identify the mechanisms that enabled and limited piecework historically, and
identify whether on--demand work faces the same pitfalls or might differentiate itself.
This approach introduces theoretical grounding that can help address
some of the most pernicious questions in crowd work,
and suggests design interventions that learn from history
rather than repeat it.
\end{abstract}
\end{document}

>>>>

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
  \externaldocument{complexity}
  \externaldocument{relationships}
  \externaldocument{decomposition}
}

\begin{document}
\onlyinsubfile{\plaintitle}
\begin{abstract}
\ali{I want to do a substantial revision of this.
We haven't touched it much throughout the whole paper's revision process, and
now I'm not so sure that this abstract is
as clear or focused on precisely what the paper contributes.}

The internet is empowering the rise of
crowd work,
gig work, and
other forms of on--demand labor.
A large and growing body of scholarship has attempted to predict
the socio--technical outcomes of this shift, especially addressing three questions:
\begin{inlinelist}
\item \nameref{sec:complexity}?,
\item \nameref{sec:decomposition}?, and
\item \nameref{sec:relationships}?
\end{inlinelist}
In this paper, we look to the historical scholarship on piecework
--- a similar trend of
work decomposition,
distribution, and
payment that was popular at the turn of the \nth{20} century ---
to understand how these questions might play out with modern on--demand work.
We identify the mechanisms that enabled and limited piecework historically, and
identify whether on--demand work faces the same pitfalls or might differentiate itself.
This approach introduces theoretical grounding that can help address
some of the most persistent questions in crowd work,
and suggests design interventions that learn from history
rather than repeat it.
\end{abstract}
\end{document}

### 2017-01-10 drafts/labor/cases.tex
chinmay's suggestions integrated

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Research Questions}

{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing.}
This has largely involved iteratively
identifying barriers to high-quality, complex work, then
overcoming them through novel designs of systems, work--flows and processes (e.g.~\cite{bernsteinSoylent,foundry,crowdForgeKittur}).
The question 
has become \textit{whether} there are limits to on--demand work,
and if so, what factors determine them.
To this question, a number of contributions to the field have pressed for answers.

@@

\notinsubfile{
  \subfile{complexity.tex}
  \subfile{decomposition.tex}
  \subfile{relationships.tex}
}
\onlyinsubfile{
  \printbibliography{}
}

>>>>

\documentclass[trackingWork]{subfiles}

\begin{document}
\section{Research Questions}

\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing.}
This has largely involved iteratively
identifying barriers to high-quality, complex work, then
overcoming them through novel designs of systems, work--flows and processes (e.g.~\cite{bernsteinSoylent,foundry,crowdForgeKittur}).
The question 
has become \textit{whether} there are limits to on--demand work,
and if so, what factors determine them.
To this question, a number of contributions to the field have pressed for answers.

@@

\notinsubfile{
  \subfile{complexity.tex}
  \subfile{decomposition.tex}
  \subfile{relationships.tex}
}

\onlyinsubfile{
  \printbibliography{}
}

### 2017-01-10 drafts/labor/complexity.tex
chinmay's suggestions integrated

\topic{It is now clear that this computational workflow approach works with some classes of complex tasks, but
the broader wicked problems largely remain unsolved~\cite{rittel1973dilemmas}.}
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering~\cite{chilton2013cascade},
categorization~\cite{andre2014crowd}, and
outlining~\cite{luther2015crowdlines}
are possible, but there is no general solution for sense--making.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.

@@

\subsubsection{\pieceworkpers}

\begin{comment}
- Farm workers-->textile
- Limit: human management and oversight
- Evaluation
- Skilled work harder
- Only some organizations can use it
- Management practices
\end{comment}

>>>>

\topic{It is now clear that this computational workflow approach works with some classes of complex tasks, but
the broader wicked problems largely remain unsolved.}
As a first example,
idea generation shows promise~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
but there is as yet no general crowdsourced solution for
the broader goal of invention and innovation~\cite{fuge2014analysis}.
Second,
focused writing tasks are now feasible~\cite{Kim2017,bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169,writingMicroTasks,agapie2015crowdsourcing}, but
there is no general solution to create
a cross--domain, high--quality crowd--powered author. 
Third,
data analysis tasks such as
clustering~\cite{chilton2013cascade},
categorization~\cite{andre2014crowd}, and
outlining~\cite{luther2015crowdlines}
are possible, but there is no general solution for sense--making.
It is not yet clear what insights would be required
to enable crowdsourced solutions for these broader wicked problems.

@@

\subsubsection{\pieceworkpers}
\begin{comment}
- Farm workers-->textile
- Limit: human management and oversight
- Evaluation
- Skilled work harder
- Only some organizations can use it
- Management practices
\end{comment}

### 2017-01-10 drafts/labor/conclusion.tex
revisions of the discussion and conclusion
table in discussion is maybe done
chinmay's suggestions integrated

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother

@@

\begin{document}
\section{Conclusion}
On--demand work is not new, but a contemporary instantiations of piecework.
In this paper, we reconsider three major research questions in on--demand work using the lens of piecework:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?'';
  \item ``\namerefl{sec:decomposition}?''; and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern on--demand work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

>>>>

\documentclass[trackingWork]{subfiles}

@@

\begin{document}
\section{Conclusion}
\topic{On--demand work is not new, but a contemporary instantiations of piecework.}
In this paper, we reconsider three major research questions in on--demand work using the lens of piecework:
\begin{inlinelist}
  \item \nameref{sec:complexity}?
  \item \nameref{sec:decomposition}?
  \item \nameref{sec:relationships}?
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern on--demand work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

### 2017-01-10 drafts/labor/decomposition.tex
apparently a typo I forgot to check in
deleting stuff
chinmay's suggestions integrated

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
% \onlyinsubfile{
% \usepackage{xr--hyper}
% \usepackage{hyperref}
% \externaldocument{complexity}
% \externaldocument{relationships}
% % \externaldocument{decomposition}
% }
\begin{document}

@@

% \onlyinsubfile{\clearpage}
\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work
consist of creative methods for decomposing goals.}
Even when tasks such as writing and editing cannot be reliably performed by individual workers,
researchers demonstrated that
decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,
bernsteinSoylent,
writingMicroTasks,
Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows,
which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g.,
a paragraph topic~\cite{crowdForgeKittur},
an error~\cite{bernsteinSoylent},
or a concept~\cite{Yu2016a,Yu2016b}) and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas,
including food labeling~\cite{noronha2011platemate},
brainstorming~\cite{siangliulue2015toward,yu2014distributed},
and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

@@

\topic{As the additional context necessary to complete a task diminishes,
the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT.
Workers seek out good requesters~\cite{martin2014being} and then 
``streak'' to perform many tasks of that same type~\cite{taskSearch}.
%and some work has gone into ameliorating the problems specific to this work site (\textit{ReLauncher}),
Researchers have reacted by designing task recommendation systems~\cite[e.g.][]{Cosley:2007:SUI:1216295.1216309}
and minimizing the amount of time that people need to spend doing anything other than
the work for which they are paid~\cite{callison2014crowd}.

\onlyinsubfile{\clearpage}
\subsubsection{\pieceworkpers}

@@

\topic{Four major stages characterize decomposition in the history of piecework.}
The first stage was decomposition of an expert task such that it could be done by non-experts. 
This was arguably the main innovation of Airy's human computers.
Rather than hire expert computers, Airy identified ways to break down astrological calculations into steps that could be completed with only a basic knowledge of mathematics.
%\topic{Decomposability is core to piecework: one cannot pay by the piece unless the pieces are small and discretizable.}
Likewise, \citeauthor{Brown01041990} argued that piecework arose in industries where there was significant task homogeneity and low fixed costs of machinery and training~\cite{Brown01041990}.
%In other words, if tasks could be clearly decomposed and defined, and if the firm could afford the training and machinery for the pieceworkers, piecework tended to be adopted.

@@

Third, decomposition led to quantification and scientific management.
What can be modularized can be measured, and what can be measured can be optimized.
With \citeauthor{taylor1914principles}'s formalization of scientific management in \textit{Taylorism}
(and Henry Ford's eponymously named \textit{Fordism}),
piecework in the early and mid--\nth{20} century surged, especially in industrial work.
Scientific management promised that the careful measurement of workers would yield
higher efficiency and output~\cite{taylor1914principles,towardsGlobalFordism}.
While \citeauthor{Brown01041990} points out that
piecework dramatically advanced the instrumented measurement of workers,
in \citeauthor{taylor1914principles}'s time highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
Instead, managers conducted ``stop watch time studies''~\cite{nadworny1955scientific},
using completion times to inform per--task compensation,
similarly to the efficiency experts hired in the Santa Fe Railway, but
substantially more precise.
The distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

@@

%\topic{Piecework researchers enumerate a number of problems with the decomposition of work,
%and the conflicting pressures managers and workers put forth.}
%\citeauthor{bewley1999wages} in particular points out that
%the approach of paying workers by the piece is
%``\dots~not practical for workers doing many tasks,
%because of
%the cost of establishing the rates and because
%piecework does not compensate workers for time spent switching tasks''.
%Ultimately, \citeauthor{bewley1999wages} argues that
%``[piecework is] infeasible,
%because~\dots~total output is the joint product of varying groups of people''~\cite{bewley1999wages}.
%To \citeauthor{bewley1999wages}, the main limiter was the ability to define and measure the work.

\onlyinsubfile{\clearpage}
\subsubsection{\whatchanged}
\begin{comment}
outline
	- measurement is more precise,
  so decomposition is deeper
	- not a single position,
  but a marketplace
\end{comment}

\topic{Where measurement and instrumentation were limiting factors for historical piecework,
computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable,
but trivial~\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
preventing scientific management from being fully utilized,
modern crowd work is measuring and modeling every click,
scroll,
and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

@@

%Third,
%modern crowd work has sliced work to such small scales that the marginal activities
%--- things like finding work and cognitive task switching ---
%have become large relative to the tasks themselves~\cite{taskSearch}.
%In the historical case of piecework,
%moving metallurgical tools,
%mining equipment,
%or
%other industry materials would have been prohibitively difficult and slow;
%workers were encouraged to specialize in a single set of tasks,
%allowing pieceworkers to sequence their tasks optimally on their own~\cite{hart2013rise}.
%The result is that on--demand workers are more free agents than historically was the case.
%However,
%because they spend significant time searching for tasks,
%the piece rate is less a good estimate of take--home earnings than before.

\onlyinsubfile{\clearpage}
\subsubsection{\implication}
If decomposition in piecework progressed in four stages, we have seen three of them in on--demand work so far.
First, as with piecework, on--demand work began by decomposing tasks so that anyone could complete them, as with data labeling on Amazon Mechanical Turk.
Second, we began to modularize and measure external expertise (e.g., software engineering, design) so that it could be brought into crowdsourcing systems~\cite{foundry,Chen2016}.
Third, we used measurement to mathematically optimize workers' behaviors so that we could make the systems more efficient~\cite{weld2010decision}.

The fourth stage, then, appears likely to occur: narrow training of workers for expert tasks. 
There is demand for skilled workers in many crowdsourcing tasks, and systems to help train workers~\cite{suzukiAtelier}. 
We might expect to see the rise of systems that scaffold workers into extremely narrow areas of expertise.

Finally, improved measurement and lowered costs of production have made it feasible to apply piecework methods to many domains where it may not have historically been possible.
The limit is no longer measurement precision, but human cognition. 
%as \citeauthor{10.2307/23702539} argues,
%then modern on--demand work stands to become far more finely--sliced and highly decomposed than ever before.
%Online tools make measurement and validation so easy~\cite{rzeszotarski2011instrumenting} that these aspects of piecework are solved,
%or near enough that they no longer limit task decomposition.
%Now,
%not just tasks,
%but entire workers' histories~\cite{hata2017glimpse},
%can be collected and analyzed in detail.
Task switching and other cognitive costs make it difficult
to work on tasks so far decontextualized from their original intention~\cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context,
and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context
--- for example,
logo design requires a deep understanding of the client and their goals.
%In part due to this limitation,
%99designs workers often recycle old designs rather than make new ones for each client~\cite{araujo201399designs}.

%So,
%ultimately,
%the levels of decomposition are likely to follow the contours of context required.
%Low--context work will be extremely highly decomposed.
%High--context work will continue to be limited.

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }

>>>>

\documentclass[trackingWork]{subfiles}
\begin{document}

@@

\subsubsection{\crowdworkpers}
\topic{Many contributions to the design and engineering of crowd work
consist of creative methods for decomposing goals.}
Even when tasks such as writing and editing cannot be reliably performed by individual workers,
researchers demonstrated that
decompositions of these tasks into workflows can succeed~\cite{crowdForgeKittur,
bernsteinSoylent,
writingMicroTasks,
Nebeling:2016:WCW:2858036.2858169}. 
These decompositions typically take the form of workflows,
which are algorithmic sequences of tasks that manage interdependencies~\cite{Bigham2014}. 
Workflows often utilize a first sequence of tasks to identify an area of focus (e.g.,
a paragraph topic~\cite{crowdForgeKittur},
an error~\cite{bernsteinSoylent},
or a concept~\cite{Yu2016a,Yu2016b}) and a second sequence of tasks to execute work on that area. 
This decomposition style has been successfully applied across many areas,
including food labeling~\cite{noronha2011platemate},
brainstorming~\cite{siangliulue2015toward,yu2014distributed},
and accessibility~\cite{lasecki2013chorus,lasecki2012real,Lasecki2011}.

@@

\topic{As the additional context necessary to complete a task diminishes,
the invisible labor of \textit{finding} tasks~\cite{martin2014being} has arisen as a major issue.}
\citeauthor{taskSearch} illustrate the task search challenges on AMT~\cite{taskSearch}.
Workers seek out good requesters~\cite{martin2014being} and then 
``streak'' to perform many tasks of that same type~\cite{taskSearch}.
Researchers have reacted by designing task recommendation systems (e.g.~\cite{Cosley:2007:SUI:1216295.1216309})
and minimizing the amount of time that people need to spend doing anything other than
the work for which they are paid~\cite{callison2014crowd}.

\subsubsection{\pieceworkpers}

@@

\topic{Four major stages characterize decomposition in the history of piecework.}
The first stage was decomposition of an expert task such that it could be done by non-experts. 
This was arguably the main innovation of Airy's human computers.
Rather than hire expert computers, Airy identified ways to break down astrological calculations into steps that could be completed with only a basic knowledge of mathematics.
Likewise, \citeauthor{Brown01041990} argued that piecework arose in industries where there was significant task homogeneity and low fixed costs of machinery and training~\cite{Brown01041990}.

@@

Third, decomposition led to quantification and scientific management.
What can be modularized can be measured, and what can be measured can be optimized.
With \citeauthor{taylor1914principles}'s formalization of scientific management in \textit{Taylorism}
(and Henry Ford's eponymously named \textit{Fordism})~,
piecework in the early and mid--\nth{20} century surged, especially in industrial work.
Scientific management promised that the careful measurement of workers would yield
higher efficiency and output~\cite{taylor1914principles,towardsGlobalFordism}.
While \citeauthor{Brown01041990} points out that
piecework dramatically advanced the instrumented measurement of workers,
in \citeauthor{taylor1914principles}'s time highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
Instead, managers conducted ``stop watch time studies''~\cite{nadworny1955scientific},
using completion times to inform per--task compensation,
similarly to the efficiency experts hired in the Santa Fe Railway, but
substantially more precise.
The distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

@@

\subsubsection{\whatchanged}
\begin{comment}
outline
	- measurement is more precise,
  so decomposition is deeper
	- not a single position,
  but a marketplace
\end{comment}

\topic{Where measurement and instrumentation were limiting factors for historical piecework,
computation has changed the situation so that a dream of scientific management and Taylorism
--- to measure every motion at every point throughout the workday and beyond ---
is not only doable,
but trivial~\cite{waltz2012quantified}.}
Where \citeauthor{10.2307/23702539} directly implicates measurement as
preventing scientific management from being fully utilized~\cite{10.2307/23702539},
modern crowd work is measuring and modeling every click,
scroll,
and keyboard event~\cite{rzeszotarski2011instrumenting,rzeszotarski2012crowdscape}.
The result is that on--demand work can articulate and track far more carefully than piecework historically could.

@@

\subsubsection{\implication}
If decomposition in piecework progressed in four stages, we have seen three of them in on--demand work so far.
First, as with piecework, on--demand work began by decomposing tasks so that anyone could complete them, as with data labeling on Amazon Mechanical Turk.
Second, we began to modularize and measure external expertise (e.g., software engineering, design) so that it could be brought into crowdsourcing systems~\cite{foundry,Chen2016}.
Third, we used measurement to mathematically optimize workers' behaviors so that we could make the systems more efficient~\cite{weld2010decision}.

The fourth stage, then, appears likely to occur: narrow training of workers for these decomposed expert tasks. 
There is demand for skilled workers in many crowdsourcing tasks, and systems to help train workers~\cite{suzukiAtelier}. 
We might expect to see the rise of systems that scaffold workers into extremely narrow areas of expertise.

Finally, improved measurement and lowered costs of production have made it feasible to apply piecework methods to many domains where it may not have historically been possible.
The limit is no longer measurement precision, but human cognition. 
Task switching and other cognitive costs make it difficult
to work on tasks so far decontextualized from their original intention~\cite{delayAndOrderLasecki}.
There will of course be tasks that can be decomposed without much context,
and these will form the most fine--grained of microtasks.
However, other tasks cannot be freed from context
--- for example,
logo design requires a deep understanding of the client and their goals.

### 2017-01-10 drafts/labor/discussion.tex
chinmay's suggestions integrated

% \msb{Shouldn't we bring up the discussion from the rebuttal about history/future connections here?}

@@

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}.
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete the task, decomposition seems a poor choice.

@@

% \onlyinsubfile{
%   \balance{}
%   \printbibliography
% }

>>>>

@@

Piecework researchers looking into decomposition pointed out long ago that
piecework is saddled by a lower limit on decomposition:
``piecework does not compensate workers for time spent switching tasks''~\cite{bewley1999wages}. % Chinmay wanted me to specifically call out that this is from chapter 6. Is that necessary...?
\ali{Chinmay: <suggestion to look at \cite{stigler1962information} and friction> --- not sure if worth getting into.}
We've since studied this phenomenon in crowd work to great length both
observationally \cite{taskSearch} and
experimentally \cite{delayAndOrderLasecki}.
We should consider whether this remains a worthwhile area to explore;
unless the work we put forth directly affects the costs of task--switching
--- for instance, the cost of suboptimal task search, or the cognitive burden of changing tasks ---
we may only make incremental advances in micro--task decomposition.
When the cognitive cost of understanding a task and its inputs outstrips the effort required to complete the task, decomposition seems a poor choice.

@@

\ali{
Discussions from Slack:

Chinmay: I think the most provocative claim is ``The history of piecework suggests that the utopian and dystopian outcomes will both occur, in different parts of the world and to different people.''\\
seems contrary to the idea that marketplaces are global\\
I would also like some more thought into the Research Agenda section\\

Ali: so the dystopian and utopian claim is partly influenced by the fact that piecework seemed to affect some industries differently than others\\

Chinmay: ah ok\\
i think you could claim the same about online piecework\\
differnt industries\\

Ali: garment-makers were pretty thoroughly marginalized, but industrial metalwork led to this whole WWII phenomenon with expert training\\
mmmm\\
but now it's not just about the industry, but about the design of the labor market\\
we can influence the ``architecture'' in a way that we couldn't before\\
this is all lessig and stuff\\

Chinmay: oh\\
i understand\\
hmm something there\\
might poke more :)

\dotfill

Chinmay> i wish you had a little more criticality in taylorism but I'm a downer :)

Ali> actually a reviewer wanted more on taylorism but i was afraid that we just didn't have the space to really give anyone into taylorism what they want

Chinmay> essentially that would be a great place to talk about how those three questions you mentioned interact

Ali> oh
that might be worth fitting in
i mean we inexplicably got it down to 9.5 pages or so
or 9.75
we were over for like 99% of the drafting and then inexplicably something just imploded and we got like half a page
so yeah i'll try and write something giving taylorism more space and using that to talk about the confluence of these three questions
}

### 2017-01-10 drafts/labor/piecework_lit.tex
chinmay's suggestions integrated

\topic{Piecework may have started in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took hold in farm work~\cite{hughRaynbirdTaskWork},
in textiles~\cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads~\cite{Brown01041990}, and 
elsewhere in manufacturing~\cite{10.2307/3827491}.
Fordism and scientific management thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.

\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in \citeauthor{hughRaynbirdTaskWork}'s essay on piecework,
particularly driven toward encapsulating the manual labor of farmwork.}
\citeauthor{hughRaynbirdTaskWork} does this by contrasting with the ``day--labourer'' ---
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} defines it through examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing offers an intuitive sense of piecework;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

\topic{We see this sense of independence in myriad times, locales, and industries.}
\citeauthor{10.2307/3827491} offers a look into the lives and culture of ``match--girls''
--- young pieceworkers, mostly women, who assembled matchsticks in the late \nth{19} century.
Of interest was their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
\citeauthor{10.2307/27508091} document piecework from 1850 through 1930 in Australia,
finding similar notions of independence and autonomy among piecework newspaper compositors:
``If a piece--work compositor~\dots~decided that he did not want to work on a particular day or night,
the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
This sense of independence and autonomy appears to be a common component of piecework.

\topic{Since workers could now choose their own schedule and style, there arose a discussion on how best to manage pieceworkers.}
This conversation generally regarded workers antagonistically~\cite{roy1954efficiency}, a far cry from the earlier rhetoric on piecework, which promised that
piece workers would gladly work as diligently and as hard as possible because
incentive--based pay rewards hard work~\cite{clark1908cotton}.
\ali{\citeauthor{norton1900textile} talks about guarding against collusion among workers, hence the instinct to include it, but
with \citeauthor{clark1908cotton}'s paper coming out in \citeyear{clark1908cotton} and \citeauthor{norton1900textile} in \citeyear{norton1900textile}, I guess the timing looks weird.}

@@

\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.

@@

Workers could, in principle, assemble as much or as little clothing as they wanted;
the reality was more grim, as
\citeauthor{riisOtherSideLives} documented in ``\citetitle{riisOtherSideLives}'' in \citeyear{riisOtherSideLives}~\cite{riisOtherSideLives}.
He found that
workers endured bleak living conditions and
worked long hours attempting to scrape together a living.

>>>>

\topic{Piecework may have started in the intellectual domain of astronomical calculations and projections,
but it found its foothold in manual labor.}
Piecework took hold in farm work~\cite{hughRaynbirdTaskWork},
in textiles~\cite{restructuringPieceworkBaker,riisOtherSideLives},
on railroads~\cite{Brown01041990}, and 
elsewhere in manufacturing~\cite{10.2307/3827491}.
At the turn of the \nth{20} century, \citeauthor{taylor1914principles}
--- a mechanical engineer with a fascination in work efficiency ---
began studying and formalizing the decomposition, tracking, and management of tasks.
In \citeyear{taylor1914principles} he published \citetitle{taylor1914principles},
concretizing an idea that had nebulously been forming,
and which he had been working out himself, for years~\cite{taylor1914principles}.
Scientific Management (and Fordism) thrust piecework into higher gear, especially as
mass manufacturing and
a depleted wartime workforce forced industry to find new ways to eke out more production capacity.

\ali{Somewhere here(?) I want to talk about Gibreth's works~\cite{gilbreth1911motion,gilbreth1911motion}. Should I save it to be the saving grace in the discussion?}

\topic{By \citeyear{hughRaynbirdTaskWork} we find
a concise definition of piecework
in \citeauthor{hughRaynbirdTaskWork}'s essay on piecework,
particularly driven toward encapsulating the manual labor of farmwork.}
He does this by contrasting with the ``day--labourer'' ---
``the chief difference lies between the day--labourer,
who receives a certain some of money~\dots~for his day's work,
and the task--labourer, whose earnings depend on the quantity of work done''~\cite{hughRaynbirdTaskWork}.
\citeauthor{10.2307/2338394} defines it through examples:
``payment is made for each hectare which is pronounced to be well ploughed~\dots~for each living foal got from a mare;~\dots~for each living calf got''~\cite{10.2307/2338394}.
This framing offers an intuitive sense of piecework;
``payment for results,'' as he calls it,
is not only common in practice, but
well--studied in labor economics as well~\cite{Figlio2007901,weitzman1976new,10.2307/3003414,BJIR:BJIR038}.

@@

\topic{We see this sense of independence in myriad times, locales, and industries.}
\citeauthor{10.2307/3827491} offers a look into the lives and culture of ``match--girls''
--- teenage women who assembled matchsticks in the late \nth{19} century in London. % added that these women were in London since Chinmay critiqued that we're glossing over the labor advocacy movement that grew in Europe, which revealed that we completely left out the fact that this all happened in England.
\ali{Chinmay: but still not convinced; this is a post hoc ergo propter hoc argument}
Of interest was their reputation ``\dots~for generosity, independence, and protectiveness,
but also for brashness, irregularity, low morality, and little education''~\cite{10.2307/3827491}.
\citeauthor{10.2307/27508091} document piecework from 1850 through 1930 in Australia,
finding similar notions of independence and autonomy among piecework newspaper compositors:
``If a piece--work compositor~\dots~decided that he did not want to work on a particular day or night, the management recognised his right to put a `substitute' or `grass' compositor in his place''~\cite{10.2307/27508091}.
This sense of independence and autonomy appears to be a common component of piecework.

\topic{Since workers could now choose their own schedule and style, there arose a discussion on how best to manage pieceworkers.}
This conversation generally regarded workers antagonistically~\cite{roy1954efficiency}, a far cry from the earlier rhetoric on piecework, which promised that
piece workers would gladly work as diligently and as hard as possible because
incentive--based pay rewards hard work~\cite{clark1908cotton}.

@@

\citeauthor{clark1908cotton} observed textile mill pieceworkers and reported,
``When he works by the day the Italian operative wishes to leave before the whistle blows,
but if he works by the piece he will work as many hours as it is possible for him to stand''~\cite{clark1908cotton}.
\end{comment}

@@

Workers could, in principle, assemble as much or as little clothing as they wanted;
the reality was more grim, as
\citeauthor{riisOtherSideLives} documented in \textit{How the Other Half Lives} in \citeyear{riisOtherSideLives}~\cite{riisOtherSideLives}.
He found that
workers endured bleak living conditions and
worked long hours attempting to scrape together a living.
